Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/high-assurance-contracts.tex
Revise to match pascalish version

    eq isPending : bool = Since(not rsp, req and not rsp);*\label{line:mon-pending}*
    eq latency : int = 0 -> (if req then 0 else pre(latency) + 1);*\label{line:mon-latency}*

    eq policy : bool = (rsp => req) -> *\label{line:mon-policy}*
                         (    (isPending => latency < MAX_LATENCY)
                          and (rsp => (req or pre(isPending))));
    -- stop user definitions

@@

\lineref{line:mon-pending} and \lineref{line:mon-latency}.
The monitor policy is defined by marking when a request is not
satisfied, \texttt{isPending}, and
counting the number of steps between requests, \texttt{latency}.  
The \texttt{isPending} variable is true
whenever there is a request that does not coincide with a
response--to be read as \emph{there is no response since the most recent request without a corresponding response}.  The
\texttt{latency} variable starts at zero, resets on every request, and
otherwise increments by one.

>>>>

    eq preIsPending : bool = pre(isPending);*\label{line:mon-pre-pending}*
    eq isPending : bool = Since(not rsp, req and not rsp);*\label{line:mon-pending}*
    eq latency : int = 0 -> (if req then 0 else pre(latency) + 1);*\label{line:mon-latency}*

    eq policy : bool = (rsp => req) -> *\label{line:mon-policy}*
                         (    (isPending => latency < MAX_LATENCY)
                          and (rsp => (req or preIsPending)));
    -- stop user definitions

@@

\lineref{line:mon-pre-pending}, \lineref{line:mon-pending}, and \lineref{line:mon-latency}.
The monitor policy is defined by marking when a request is not
satisfied, \texttt{isPending}, and
counting the number of steps between requests, \texttt{latency}.  
The \texttt{isPending} variable is true
whenever there is a request that does not coincide with a
response--to be read as \emph{there is no response since the most recent request without a corresponding response}.  The
\texttt{latency} variable starts at zero, resets on every request, and
otherwise increments by one. 
The \texttt{preIsPending} is needed to make the contract Pascalish since since the current and previous value of \texttt{isPending} are used in the definition of \texttt{policy}.

\lineref{line:mon-policy}. 
The policy makes sure the latency is bounded whenever there is a pending request, and it it makes sure that a response is a result of a request.
The initial step differentiates from later steps in only needing to be sure a response is a result of a request.
